---
title: "Shiny Application: Clustering Pitch Presentation"
date: "Monday, January 20, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	tidy = TRUE,
	tidy.opts = list(width.cutoff = 60)
)
```

## Introduction{.smaller}

This web page consists of an html format presentation. The presentation is written in R Markdown. This work was done on Monday, January 20, 2020.

This presentation will provide details on an interactive Shiny application. This application allows users to perform realtime clustering analysis on a data set.

The Shiny application was uploaded to shinyapps.io by RStudio using the 'rsconnect' function in R.

## Application Details{.smaller}

This application deploys k-means as a clustering method using the built-in 'kmeans' function in R.

This application uses the 'rock' dataset in R. This dataset consists of measurements on 48 rock samples from a petroleum reservoir. Twelve core samples from petroleum reservoirs were sampled by 4 cross-sections. Each core sample was measured for permeability, and each cross-section has total area of pores, total perimeter of pores, and shape. The four numeric features in the dataset are described below.

'area' - area of pores space, in pixels out of 256 by 256

'peri' - perimeter in pixels

'shape' - perimeter/sqrt(area)

'perm' - permeability of core sample

## Links and Usage{.smaller}

The Shiny application is hosted at the following link.

https://pvb11.shinyapps.io/shinyapp/

This clustering application is interactive. The user can select which variables to compare, as well as the number of clusters to display.

All of the R code used for this project is found in the following git repository in the server.R and ui.R files. Users can also find complete documentation and other files in this repository.

https://github.com/pvb11/Course9_Assignment3

## Code Display{.smaller}

Here is a look at the server.R calculations that are being performed.

```{r echo=FALSE}
function(input, output, session) {
  selectedData <- reactive({
    rock[, c(input$xcol, input$ycol)]
  })
  clusters <- reactive({
    kmeans(selectedData(), input$clusters)
  })
  output$plot1 <- renderPlot({
    palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
              "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999"))
    par(mar = c(5.1, 4.1, 0, 1))
    plot(selectedData(),
         col = clusters()$cluster,
         pch = 20, cex = 3)
    points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
  })
}
```
